Brownian Dynein Model

### 2015-08-22 latex/derivation.tex

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{t}\cos(\Theta_{mr}-\pi) = X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr}+L_{s}\cos(\Theta_{br}-\pi) = X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}
